The Weakly Nonlinear Saturation of the Magnetorotational Instability

### 2014-09-12 paper/mri_paper.tex
bib file and renamed paper

The magnetorotational instability (MRI) arises in a differentially rotating disk with a vertical magnetic field.

@@

>>>>

The magnetorotational instability (MRI) is the leading candidate for rapid angular momentum transport in astrophysical disks. The instability arises when a differentially rotating disk is threaded by a vertical magnetic field (\citei{CHANDRASEKHAR:1960wh}). The presence of the magnetic field destabilizes the disk gas, driving turbulence and angular momentum transport.

The MRI evolves via a period of linear growth, followed by nonlinear saturation. The saturation mechanism is not well understood.

@@

%\bibliographystyle{yahapj}
\bibliography{mri.bib}
